Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-03-18 main.tex
Update on Overleaf.

%mm3 [Proposed new title]
\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
%mm3 \title{Simulating an Isolated Dwarf Galaxy with Individual Star Feedback and Chemistry}
%\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution}
%Unstable Star Formation for the Lowest Mass Dwarf Galaxies
\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg L. Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

@@

\begin{abstract}
%\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. added wind caveat. removed large H2 content mention (should I put this last one back?).}
%Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows. However, we are far from a complete understanding of feedback and galactic chemodynamics in general. 
In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at 
%mm3 high resolution ($\sim$ few pc) 
   grid resolutions of only a few parsecs 
in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including %stellar winds from massive and asymptotic giant branch stars,
%mm3 AGB
    asymptotic giant branch 
winds, 
photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. 
%mm3 [moved below] {\bf We additionally include stellar winds from massive stars, but reduce their velocity due to computational constraints.}
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
We furthermore follow the star-by-star 
%mm3 stellar 
      chemical
yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
%mm3 
    We include the yields ejected in massive stellar winds, but neglect the winds' energetic contribution due to computational 
    constraints.
 We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the
%mm3 differences with which individual metal species mix and evolve 
    variation in mixing behavior of individual metal species
within the 
%mm3 ISM.
     multi-phase interstellar medium.

%Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions.

% mm: conclusion of this discussion should perhaps be mentioned
%% AE (reply): reworded slightly but still have no detailed mention of this.
\end{abstract}

@@

However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}. In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution 
%mm3 or additional viscosity [I'm not sure I understand this.  Adding explicit viscosity will increase mixing, although it at least places it on a physical basis, rather than relying on error terms with unphysical scale dependences.]
to reduce. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

Increasing physical resolution reduces reliance on sub-grid physics for mixing.  However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}. Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations. This is acutely problematic at star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$). Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.  The most straightforward
solution is to remove the single stellar population formalism entirely and simply track stars as individual particles. %which we do here

@@

As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}. To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.  We have made these new tables public in the main \texttt{Grackle} repository. These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
%mm3 {\bf {\it (addressing MM's comment below (I was unable to find a ref. where this was accounted for)}: 
Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates. 
%}
%%mm2 
%   {\bf [MM: I'm a bit confused here: how does the ISRF interact with the cooling?  Shouldn't that move you around in the Cloudy tables, possibly quite substantially?]}

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on 
%mm3 galaxy 
    galacitc
scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$. No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.

We make the common ansatz that star formation occurs by converting 
%mm3 some fraction of 
gas into stars in a free fall time $\tau_{\rm ff}$ 
%mm3 characterized by 
   with 
a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, 
the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).

@@

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z
%mm3 [confirm]
       / Z_{\odot} 
=$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}. This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$. We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore SN yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

@@

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe. Where this transition occurs is uncertain, but is commonly taken to be 
%mm3
     at a mass $M_{\rm trans} \sim 
8$--10~M$_{\odot}$. This is a free parameter in our model; we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics). Varying 
%mm3 $M_{\rm thresh}$ 
           $M_{\rm trans}$
changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017} explores how the choice of 
%mm3 $M_{\rm thresh}$
           $M_{\rm trans}$ affects galaxy abundances in a one-zone model. We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.

@@

Type Ia SNe are an important additional source of galactic chemical enrichment. These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams. We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}. We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, 
%mm3
     substantially limiting the number of Type Ia SNe occurring during the initial gigayear in 
     our models.

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback. We inject the feedback energy in a spherical region with a three-cell radius centered on the emitting star particle, assuming full thermalization of the wind kinetic energy. The total injected energy in timestep $\Delta t$ is therefore $E_w = \dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$. We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells. We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
%Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations.

@@

\subsubsection{Core Collapse SNe}
\label{sec: core collapse}
Stars between  $
%mm3 M_{\rm thresh}
           M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy. Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}). We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
%mm3 [How do you antialias the energy?  Something like Simpson's cloud-in-cell method, or something else?]
We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle. In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.

@@

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$. This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations. Instead, we use a 
%mm3 log-linear 
    power-law 
fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.

@@

Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This 
%mm3 additionally 
prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation. 
%mm3 These 
    During this period, 
SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances. We note that this initial driving is somewhat ad hoc in that we do not include any other effects from the stellar population that would have caused these SNe.

%mm3 {\bf New (addressing KVJ's comment to clarify how to interpret / what is target comparison point for our galaxy model:} 
We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales. In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations. Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances. In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution. Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe. The subsequent metal enrichment from the stars in our simulation can be thought of as
%mm3
    tracking 
a change in abundances
%mm3 , or delta abundances, 
from arbitrary initial conditions. We 
%mm3
   will 
discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.

\section{Results}
\label{sec:results}
We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first 
%mm3
   new
star forms. Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual 
%mm3 initialization of the simulation
   beginning of the simulation run. 
The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical heigh $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy. We include a resolution study in Appendix \ref{appendix:resolution_study}.

>>>>

\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}

\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg L. Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

@@

\begin{abstract}
%\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. added wind caveat. removed large H2 content mention (should I put this last one back?).}
%Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows. However, we are far from a complete understanding of feedback and galactic chemodynamics in general. 
In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We include the yields ejected in massive stellar winds, but neglect the winds' energetic contribution due to computational constraints. We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
\end{abstract}

@@

However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}. In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution to reduce. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

Increasing physical resolution reduces reliance on sub-grid physics for mixing.  However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}. Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations. This is acutely problematic at star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$). Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.  The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.

@@

As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}. To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.  We have made these new tables public in the main \texttt{Grackle} repository. These are discussed in greater detail in Appendix ~\ref{appendix:cooling}. Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on galacitc scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$. No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.

We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.

@@

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}. This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$. We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore SN yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

@@

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe. Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$. This is a free parameter in our model; we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model. We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.

@@

Type Ia SNe are an important additional source of galactic chemical enrichment. These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams. We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}. We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback. We inject the feedback energy in a spherical region with a three-cell radius centered on the emitting star particle, assuming full thermalization of the wind kinetic energy. The total injected energy in timestep $\Delta t$ is therefore $E_w = \dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$. We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells. We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).

@@

\subsubsection{Core Collapse SNe}
\label{sec: core collapse}
Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy. Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}). We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions. 
% AE: responding to mm3, this avoids aliasing:
We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid. We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle. In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.

@@

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$. This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations. Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.

@@

Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation. During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances. We note that this initial driving is somewhat ad hoc in that we do not include any other effects from the stellar population that would have caused these SNe.

We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales. In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations. Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances. In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution. Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe. The subsequent metal enrichment from the stars in our simulation can be thought of as tracking 
a change in abundances from arbitrary initial conditions. We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.

\section{Results}
\label{sec:results}
We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms. Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run. The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical heigh $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy. We include a resolution study in Appendix \ref{appendix:resolution_study}.
